Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-05 ms.tex
gcm done

%	spin-orbit alignment: 2016ApJ...823...29A

@@

%Phase curve observation to provide context for the global thermal structure of the planet.

@@

\begin{deluxetable}{ccccc}
\label{tab:photometry}
	%\tabletypesize{\small}
	\tablenum{1}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} }% \\

%		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
%		\colhead{(mag)} & \colhead{(mag)}}%   \\

	%	\colhead{(1)} & \colhead{(2)} & \colhead{(3)} &
	%	\colhead{(4)} & \colhead{(5)}  
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

@@

%As discussed in \S \ref{sec:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise. To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters). We fit  
%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).  %The shading denotes the  1\,$\sigma$ confidence interval on the best fit. 
We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\begin{deluxetable}{llllll}
\label{tab:model_comparison}
	\tablecolumns{6}
	\tablewidth{0pt}
	\tablecaption{Model Comparison \label{table:models}}
	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

\subsection{Phase Curve Amplitudes and Hotspot Offsets}
The shape of a phase curve can be summarized with two parameters: the amplitude of thermal phase variation (minimum to maximum brightness, divided by the secondary eclipse depth) and the location of peak brightness (typically called a ``hotspot offset" and measured in degrees eastward of the substellar point). Larger amplitudes and smaller offsets are both indicative of inefficient heat transport to the nightside.

Table\,\ref{table:amps_offsets} lists the estimated amplitudes and offsets for the phase curve fits (median and $1\,\sigma$ credible interval). These values are from the sine curve model for the thermal phase variation, which fits directly for the amplitude and hotspot offset. For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero. We note that some of the spectroscopic channels have amplitudes greater than unity, which is physically impossible (the planet cannot emit negative flux). As a sanity check, we take the weighted average over the WFC3 channels and find an average amplitude of $0.91\pm0.02$, which shows that at higher precision the results are physical and agree well with the large amplitudes observed for other hot planets \citep{komacek16}.  The \Spitzer\ phase curves also have large amplitudes (near 0.85) and hotspot offsets consistent with zero.

\begin{deluxetable}{llLL}
	\tablecolumns{4}
	\tablewidth{0pt}:
	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
	\tablehead{
		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset)}\\
	\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}
		\startdata
		WFC3 & data & 0.91 \pm 0.02 & -0.3 \pm 0.1 \\
		\, & nominal GCM & 0.89 & 15.32 \\
		\, & [Fe/H] = 0.5 GCM & 0.84 & 19.64 \\
		\, & $\tau_\mathrm{drag4}$ GCM & 0.97 & 2.34 \\
		\, & $\tau_\mathrm{drag3}$ GCM & 0.99 & 0.18 \\
		Spitzer 3.6 $\mu$m & data & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
		\, & nominal GCM & 0.78 & 9.19 \\
		\, & [Fe/H] = 0.5 GCM & 0.72 & 12.79 \\
		\, & $\tau_\mathrm{drag4}$ GCM & 0.86 & 0.90 \\
		\, & $\tau_\mathrm{drag3}$ GCM & 0.97 & 0.18 \\
		Spitzer 4.5 $\mu$m & data & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
		\, & nominal GCM & 0.79 & 8.11 \\
		\, & [Fe/H] = 0.5 GCM & 0.73 & 11.35 \\
		\, & $\tau_\mathrm{drag4}$ GCM & 0.85 & 0.90 \\
		\, & $\tau_\mathrm{drag3}$ GCM & 0.93 & 0.18 \\
		\enddata
	\end{deluxetable}

@@

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar. FIXME say here what the temperature difference is at substellar point.}
\label{fig:model_comparison}
\end{figure*}

@@

\subsection{Comparison of Thermal Phase Variation Models}
We compared four different models for the thermal phase variation: a sinusoid and three temperature maps. The sinusoid has been widely used to model phase variation in previous analyses \citep[e.g.][]{knutson09, stevenson14}. One advantage of the sinusoid model is that it directly fits the phase variation amplitude and offset from the substellar point, and can be inverted to map the climate \citep{cowan08}. Fitting temperature maps directly is a new approach enabled by the \texttt{SPIDERMAN} package.  We consider three parameterizations for the temperature map, which each have different strengths. One is a physically-motivated kinematic model that closely reproduces GCM simulations \citep{zhang17}.  The second parameterization is a spherical harmonic map, which is the most flexible model we consider and makes the fewest assumptions about the true climate. The third model has just two free parameters, a dayside temperature and a nightside temperature. This model is easiest to compare to one-dimensional forward models of the dayside, which assume a uniform temperature/pressure profile.

All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

%Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.

The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection. The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}. The sinusoid has eight free parameters (amplitude, phase offset, eclipse duration, ingress/egress duration, and midpoint and depth for each of two eclipses), whereas the spherical harmonics model has four (for degree two).  The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).  As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model overpredicts the nightside flux, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside. 
%The spherical harmonics model is strongly favored for most of the data sets according to the AIC and BIC. It has slightly more free parameters than the other models (four, versus three for the kinematic model and two for the two-temperature model).

We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude. The kinematic model has the hottest dayside temperature and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$. %For the WFC3 data, the peak temperature ranges from $2890$ to $3960$ K, and the minimum ranges from $0$ to $1980$ K.

These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient, and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

@@

%The spherical harmonics model fits better according to the BIC and the AIC; however, it yields higher temperatures at the poles than at the equator, which does not agree with predictions from GCM simulations \citep{FIXME}.

@@

%\subsection{Clouds?}
\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
To interpret the phase-resolved spectra, we performed two model fits. First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to evaluate the atmospheric composition and thermal structure.

@@

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. (\textbf{Mike: citations?}) We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium \citep[calculated with the NASA CEA routine;][]{gordon94}.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, VO, FeH, and H$_2$-H$_2$ CIA. Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is an important absorber at temperatures above 2500 K \citep{arcangeli18}.  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite \citep[described in][]{line13a, line14}.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

@@

We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$. The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only). Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside. Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek16}. The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher, cooler pressure levels (\textbf{Mike: does this make sense, since the atmosphere has a thermal inversion?}).

We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated. Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point. To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m). Given that the result hinges on a single photometric band and there are no spectrally resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
%As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary.

@@

%\subsection{Climate}
%Heat redistribution, Bond albedo, inversions

%\subsection{Bond Albedo}

\section{Comparison with GCMs}
\label{sec:gcm}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).  Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.  We also ran models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.  Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field. We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales of $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$.

To assess how well the GCM predictions reproduce the data, we calculate the amplitude and hot spot offset for all the models (listed in Table\,\ref{tab:amps_offs}). The models with drag included are generally better fits, with phase variation amplitude near unity and a hot spot offset near zero for all three band-passes. The nominal model and metal-enhanced composition ([Fe/H] = 0.5) both have a phase curve offset that is too large (

Figure\,\ref{fig:gcmcomparison} shows GCM predictions compared to the best fit model to the WFC3 phase curve. The WFC3 bandpass is near the peak of the planet's thermal emission, so it provides a good test of whether the GCM reproduces the properties of the planet.

However, in the WFC3 bandpass the drag models underestimate the flux at longitudes away from the substellar point. For example, the FIXME model predicts 20\% less flux than is observed at quadrature. \textbf{Vivien: are these fast drag timescales even reasonable?}).

FIXME: change taudrag3 label. change text about unphysical phase curve ampltiude

%This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.  The models with added drag more closely reproduce the small hotspot offset that is observed. The main effect of drag is to slow down advection of heat to the nightside, which shifts the peak brightness closer to the substellar point.  The best fit WFC3 phase curve has a hotspot offset of FIXME. The drag models have offsets of $0.2$ and $2.3$ degrees for $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, compared to $15$ degrees for the nominal GCM.  The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.

We also compared the GCM output to the temperature maps retrieved with \texttt{spiderman}. Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag3}$ GCM compared to the best it models. The GCM has a minimum and maximum temperature of $920$ and $3360$ K, which is most comparable to the fit from the spherical harmonic model.  The GCM nightside temperatures are around $300$ K cooler than the spherical harmonics fit,

. The polar regions are the most discrepant, with temperatures are about $1000$ K cooler in the GCM than the spherical harmonics model. FIXME

The GCMs also provide insight into what molecules are present in which parts of the atmosphere. As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum. Figure\,\ref{fig:gcmcomposition} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM. The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.

\textbf{Vivien: did you run a cloudy model?}

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Companions}
\label{sec:comparison}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, the planet's other properties (surface gravity, rotation rate, irradiation) are different. To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions. The object properties are summarized in Table\,\ref{tab:sources}.

We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature. Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).

%TWA 22A - Bonnefoy+2014 (Bonnefoy 09), RXS - Lafren 08,10 (H magfrom Lafren 08), J1610 - Aller+13
%dist: teixeira08, 
The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}. They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, bonnefoy09, aller13} and distances \citep{gaia16}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.

>>>>

@@

@@

\begin{deluxetable}{ccccc}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103 \label{tab:photometry}}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} }
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

@@

%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).  We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\subsection{Phase Curve Amplitudes and Hotspot Offsets}
The shape of a phase curve can be summarized with two parameters: the amplitude of thermal phase variation (minimum to maximum brightness, divided by the secondary eclipse depth) and the location of peak brightness (typically called a ``hotspot offset" and measured in degrees eastward of the substellar point).  Table\,\ref{table:amps_offsets} lists the estimated amplitudes and hotspot offsets (median and $1\,\sigma$ credible interval) for the band-integrated WFC3 phase curve and both \Spitzer\ channels. The estimates are from the sine curve model for the thermal phase variation, which fits directly for the amplitude and offset.

For all three phase curves, the hotspot offset is consistent with zero degrees, indicative of a fast radiative-to-advective timescale (the incident flux is reradiated to space faster than it is advected around to the nightside). Fast radiative timescales are precicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{komacek17}.  The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution. In \S\,\ref{sec:gcm} we compare these results to expectations from 3D GCMs.

%For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero. We note that some of the spectroscopic channels have amplitudes greater than unity, which is physically impossible (the planet cannot emit negative flux). As a sanity check, we take the weighted average over the WFC3 channels and find an average amplitude of $0.91\pm0.02$, which shows that at higher precision the results are physical and agree well with the large amplitudes observed for other hot planets \citep{komacek16}.  The \Spitzer\ phase curves also have large amplitudes (near 0.85) and hotspot offsets consistent with zero.

\begin{deluxetable}{llLL}
	\tablecolumns{4}
	\tablewidth{0pt}
	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
	\tablehead{
		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset}\\
	\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}
		\startdata
		WFC3 & data & 0.91 \pm 0.02 & -0.3 \pm 0.1 \\
		\, & nominal GCM & 0.89 & 15.32 \\
		\, & [Fe/H] = 0.5 GCM & 0.84 & 19.64 \\
		\, & $\tau_\mathrm{drag4}$ GCM & 0.97 & 2.34 \\
		\, & $\tau_\mathrm{drag3}$ GCM & 0.99 & 0.18 \\
		Spitzer 3.6 $\mu$m & data & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
		\, & nominal GCM & 0.78 & 9.19 \\
		\, & [Fe/H] = 0.5 GCM & 0.72 & 12.79 \\
		\, & $\tau_\mathrm{drag4}$ GCM & 0.86 & 0.90 \\
		\, & $\tau_\mathrm{drag3}$ GCM & 0.97 & 0.18 \\
		Spitzer 4.5 $\mu$m & data & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
		\, & nominal GCM & 0.79 & 8.11 \\
		\, & [Fe/H] = 0.5 GCM & 0.73 & 11.35 \\
		\, & $\tau_\mathrm{drag4}$ GCM & 0.85 & 0.90 \\
		\, & $\tau_\mathrm{drag3}$ GCM & 0.93 & 0.18 \\
		\enddata
	\end{deluxetable}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM. We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a representative photospheric pressure of 0.01 bar.}
\label{fig:model_comparison}
\end{figure*}

@@

@@

\subsection{Climate}
We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \citep{zhang17}, and a spherical harmonic map. We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08}.  All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps. Table\,\ref{table:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves. We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.

The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection. The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}. The sinusoid has eight free parameters (amplitude, phase offset, eclipse duration, ingress/egress duration, and midpoint and depth for each of two eclipses), whereas the spherical harmonics model has four (for degree two).  The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).  As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model overpredicts the nightside flux, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.

We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude. The kinematic model has the hottest dayside temperature and the two-temperature model has the smallest. The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve. The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.  These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.  The spherical harmonics model has an intermediate temperature gradient, and fits the data the best. However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).

\begin{deluxetable}{llllll}
	\tablecolumns{6}
	\tablewidth{0pt}
	\tablecaption{Model Comparison \label{table:model_comparison}}
	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
		\startdata
		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
\end{deluxetable}

@@

@@

%\subsection{Clouds?}
\section{Atmospheric Composition and Thermal Structure}
\label{sec:composition}
We characterized the planet's atmospheric composition by fitting 1D models to the phase-resolved emission spectra.  First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features. We then performed a more sophisticated grid-based retrieval to estimate the atmospheric metallicity, carbon-to-oxygen ratio, and thermal structure.

@@

At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles. We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium \citep[calculated with the NASA CEA routine;][]{gordon94}.  We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, VO, FeH, and H$_2$-H$_2$ CIA. Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is an important absorber at temperatures above 2500 K \citep{arcangeli18}.  Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite \citep[described in][]{line13a, line14}.  We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} and interpolated in the grid to calculate the likelihood at each model step. We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).

@@

We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$. The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only). Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside. Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek17}. The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher pressure levels.

We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated. Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point. To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m). Given that the result hinges on a single photometric band and there are no spectrally resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.

%As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary.

@@

\section{Comparison with GCMs}
\label{sec:gcm}
To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: add text describing GCM}).  Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.  We also ran models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.  Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field. We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales of $\tau_\mathrm{drag} = 10^3$ and $10^4$ s. We label the drag models $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.

To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}). The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to slower wind speeds.  The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees). On the other hand, the drag models do not match the observed phase curve amplitudes (with values near unity, in contrast to the 0.8 - 0.9 that is observed). As shown in Figure\,\ref{fig:gcmcomparison}, the drag models predict the dayside planet-to-star flux fairly accurately, but underestimate the planet-to-star flux away from the substellar point. (\textbf{Vivien and others: how do we heat up the nightside to match the data better?})

We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}. Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag3}$ GCM compared to the best fit models. At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K. The temperature gradient from the dayside to the terminator is intermediate between the kinematic and spherical harmonics models. The GCM predicts a cooler nightside than all models except the two-temperature model. We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table
\,\ref{table:model_comparison}). Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.

The GCMs also provide insight into what molecules are present in which parts of the atmosphere. As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum. Figure\,\ref{fig:gcmcomparison} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM. The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.  By contrast, CO remains intact throughout the atmosphere.  Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}, but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Companions}
\label{sec:comparison}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, the planet's other properties (surface gravity, rotation rate, irradiation) are different. To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions. The object properties are summarized in Table\,\ref{table:sources}.

We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature. Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).  The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}. They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, bonnefoy09, aller13} and distances \citep{gaia16}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.
